Visualizing and Interpreting Multi-Group Confirmatory Factor Analysis

### 2023-03-30 manuscript.Rmd
so many pictures

```{r setup, include = FALSE}
library(papaja)
library(lavaan)
```

@@

Research Questions:

By the end of this tutorial manuscript, readers will: 1. Be able to create visualizations for common steps to multi-group confirmatory factor analysis. 2. Be able to interpret the impact and size of potential non-invariance on measurement. 3. Understand the impact of measurement variability on replication and generalizability.

# Methods

## Design

Data will be simulated based on a multivariate normal distribution using R. The data will include two groups of individuals for multi-group confirmatory factor analysis (ns = 250; N = 500). The latent variables will be assumed to be continuous normal, and the measured items will be simulated using a traditional 1-7 Likert-type scale, matching many of the types of scales published in psychology and Assessment. Each item will be assumed to be related to the latent variable with loadings approximately equal to .60 to .80 (minus scenarios in which configural non-invariance is simulated).

## Variables

- Number of factors: one and two latent variable models will be simulated with five measured items for each latent variable. 
- Area of invariance: a model with non-invariance at each stage will be simulated including configural, metric, scalar, and strict non-invariance. One model with complete invariance will be used for comparison purposes. 
- Size of invariance: the size of the invariance will be simulated at three levels.

none, small, medium, large 
two models
metric (loadings), scalar (intercepts), strict (residuals)

4X2X3

since these are normally tested sequentially, we will only do one at a time

https://stats.stackexchange.com/questions/593243/data-simulation-in-r-for-measurement-invariance

```{r}
model.1 <- "lv =~ q1 + q2 + q3 + q4 + q5"

model.2 <- "lv =~ q1 + q2 + q3 + q4 + q5
lv2 =~ q6 + q7 + q8 + q9 + q10
"

# Packages
library(lavaan)

# specify population model for group 1 and group 2
population_model_g1 <-'f1=~x1+.6*x2+.7*x3+0.5*x4'
population_model_g2 <-'f1=~x1+.6*x2+.7*x3+0.4*x4'

# Sumulate data
set.seed(1234)
model_data_g1<-lavaan::simulateData(population_model_g1,sample.nobs=500)
model_data_g2<-lavaan::simulateData(population_model_g2,sample.nobs=500)

# Add group label
model_data_g1$group <- "Group1"
model_data_g2$group <- "Group2"

# put data into one data frame
model_data_all <- cbind(model_data_g1,model_data_g2)

```

#### delete this 
Across all studies, results indicated that the majority of the standardized factor loading differ-
ences were below .10, and few were greater than .50. Given these results, small, medium, and large
differences in factor loadings were operationalized as .10, .20, and .30, respectively. In other words,
the factor loadings in the focal group were increased by .10, .20, or .30 to simulate MNE in various
conditions. In contrast, intercept differences in the literature were larger than the factor loading
differences, and the majority of these differences were below .20, but very few were above 1.00.
Therefore, intercept differences across groups were operationalized as .25, .50, and .75. Figures A1
and A2 in the online supplemental material show the distributions of differences between the
standardized factor loadings and intercepts in the reference and focal groups.

## Data analysis

Multi-group confirmatory factor analysis will be examined across the simulated two groups of individuals using lavaan (Rosseel, 2012) focusing on the most common procedure outlined in Brown (2015). Each stage of measurement invariance (i.e., configural, metric, scalar, and strict) will be examined in the simulated data demonstrating how to visualize results using common tools, such as ggplot2 (Wickham et al., 2021). These visualizations will be compared across differences in non-invariance size to illustrate how to interpret the size of the non-invariance. Last, these effects will be examined on total score measurement (i.e., latent means) to explore the potential impacts on replication. Finally, suggestions will be provided for framing registered reports using multi-group confirmatory factor analysis.

@@

Visualizing Measurement Model Parameters for Tests of (Non)Invariance/DIF: 
Purpose, Presentation, and a New R Package

Type: Tutorial

Authors: John K. Sakaluk, Brenton M. Wiernik, Flavio Azevedo, Alex J. Denison, and Erin M. Buchanan

Email: jsakaluk@uwo.ca

300 Word Summary: 
Latent variable psychometric theory remains psychology’s most popular framework for conceptualizing and studying psychological entities across its many subdisciplines. Indeed, psychologists regularly use latent variable analysis frameworks to generate a “measurement model”: a statistical statement of the relations between a given set of observed variables and their construct(s) when attempting to describe and quantify the substance of the theoretical entities that they study. A core--and tacit--assumption, however of latent variables is that the measurement parameters are consistent between groups or across a given continuous covariate, as divergent measurement model parameters otherwise threaten the validity of the estimation, testing, and comparison of structural parameters. Psychologists therefore are often tasked with testing to establish “measurement invariance” (or equivalently, to rule out “differential item functioning”) for their latent variables of interest. But whereas the estimation, testing, and comparison of measurement model parameters is commonplace, the visualization of these parameters is virtually nonexistent, largely owing to a dearth of any standardized manner by which these parameters ought to be depicted. Without any compelling visualization techniques, the process of evaluating measurement (non)invariance seems likely to persist in facilitating relatively uninformative all-or-none omnibus testing, without any possibility of researchers identifying meaningful patterns. We therefore propose to describe, apply, and develop supporting analytic materials (e.g., R functions and tutorials) to visualize measurement modeling parameters. Our approach will be amenable to either multi-group comparisons or continuous covariate examinations of measurement modeling parameters and will enable emphasizing particular parameters and/or variables, while also providing visual information about the model as a whole. Finally, our approach will emphasize accessibility, in terms of: 1) creating easy-to-use functions for interested users to adopt in their own work, which will create 2) publication-ready greyscale figures and/or; 3) figures in a colorblind-friendly palette.  
Prior Req’d Knowledge:
R coding
Regression
Latent variable theory and measurement modeling

What: 
Rationale
Easy-to-use functionality/package for visualizations of measurement modeling output for DIF/Noninvariance-Testing, including:
Scale of measuremen-friendly for source of noninvariance
Multi-Group
Continuous-Covariate
Multilevel(s) Targeting
Measurement parameter (loading, intercept, residuals(?))
Item level (e.g., noninvariance/DIF effect sizes?)
Test level
Application/didactic example
Existing data sets? And/or?
Simulated data sets?

Guiding Programming Values
Easy to use
Should use df and fitted lavaan object and little else
Easy to incorporate into pubs
Should have a template option for APA-compliant figures (i.e., greyscale)
Accessibility
Should have a template(s) option for beautiful and colourblind-friendly palette(s)
Modifiable
Should return ggplot2::ggplot objects that the user can modify as desired; perhaps a “basic” template option that returns the geoms_ with little else?

March 24 Meeting

Introductions

Rehash of project goals/features + Discussion
Visualization of measurement model parameters for noninvariance/DIF testing
Visualization types
Response curves (latent score X, predicted item score on Y)
IRT Sigmoidal curves
CFA item “curves” 
“Common” visualization style (simple intercepts/slopes) for MCCFA/RFA
Error variance could be a band 
Faceted by items
Test level observed score and latent score distributions
Densities with grouped observed + grouped latent scores
Variance decomposition signal:noise (communality to uniqueness) “candybar plots”
R Functions (take selection of items and group/covariate and/or MGCFA lavaan object)
Return ggplot object
Options for “canned” style (e.g., APA compliant) 
Didactic example
learnr tutorial(s)

Preferred workflow/systems
lavaan:: focused
Github repo for package
Brenton with commit access on master branch
Others suggest changes with pull requests
Github issues for communication
Use Brown terminology
Configural
Metric
Scalar
Strict

>>>>

```{r libraries, include = FALSE}
library(papaja)
library(lavaan)
library(broom)
library(dplyr)
library(ggplot2)
# devtools::install_github("psyteachr/introdataviz")
# devtools::install_github("ddueber/dmacs")
library(introdataviz)
library(dmacs)
library(cowplot)
```

```{r cfa-function, include = FALSE}
# CFA function
mgcfa <- function(data, group, model){

  group_names <- unique(data[ , group])

  model.overall <- cfa(model = model, data = data)
  model.group1 <- cfa(model = model, data = subset(data, group == group_names[1]))
  model.group2 <- cfa(model = model, data = subset(data, group == group_names[2]))
  model.configural <- cfa(model = model, data = data, group = group, meanstructure = T)
  model.metric <- cfa(model = model, data = data, group = group, group.equal = "loadings")
  model.scalar <- cfa(model = model, data = data, group = group, group.equal = c("loadings", "intercepts"))
  model.strict <- cfa(model = model, data = data, group = group, group.equal =  c("loadings", "intercepts", "residuals"))

  model_coef <- bind_rows(
    tidy(model.overall, conf.level = .95) %>% mutate(model = "overall"), 
    tidy(model.group1, conf.level = .95) %>% mutate(model = "group1"), 
    tidy(model.group2, conf.level = .95) %>% mutate(model = "group2"), 
    tidy(model.configural, conf.level = .95) %>% mutate(model = "configural"), 
    tidy(model.metric, conf.level = .95) %>% mutate(model = "metric"), 
    tidy(model.scalar, conf.level = .95) %>% mutate(model = "scalar"), 
    tidy(model.strict, conf.level = .95) %>% mutate(model = "strict")
  )

  model_fit <- bind_rows(
    glance(model.overall) %>% mutate(model = "overall"), 
    glance(model.group1) %>% mutate(model = "group1"), 
    glance(model.group2) %>% mutate(model = "group2"), 
    glance(model.configural) %>% mutate(model = "configural"), 
    glance(model.metric) %>% mutate(model = "metric"), 
    glance(model.scalar) %>% mutate(model = "scalar"), 
    glance(model.strict) %>% mutate(model = "strict")
    )

  return(list(
    "model_coef" = model_coef,
    "model_fit" = model_fit,
    "model.overall" = model.overall,
    "model.group1" = model.group1,
    "model.group2" = model.group2,
    "model.configural" = model.configural,
    "model.metric" = model.metric,
    "model.scalar" = model.scalar,
    "model.strict" = model.strict
  ))

}
```

```{r test-function, eval = F, include = F}
# temp test
data_coef = results.large.res$model_coef
model_step = "configural" 
item_name = "q4"
x_limits = c(-1,1)
y_limits = c(min(df.large.res$q4), max(df.large.res$q4))
ci_level = .95
model_results = results.invariant$model.configural
lv_name = "lv"
```

```{r plot-function, include = FALSE}
plot_mgcfa <- function(data_coef, # output from model_coef
                       model_step, # which model
                       item_name, # name of observed item
                       x_limits = c(-1,1), # LV limits to graph
                       y_limits, # Y min and max in data 
                       ci_level, # what ci do you want
                       model_results, # what model results do you want 
                       lv_name # which latent is the observed variable on
                       ){

  # calculate cutoff
  cutoff <- qt(p = (1-ci_level)/2, 
               df = sum(unlist(model_results@Data@nobs)), 
               lower.tail = F)

  # first get the data
  graph.data <- data_coef %>% # put in tidy coefficients
  filter(model == model_step) %>% # pick a model
  filter(grepl(item_name, term)) %>%  # pick a question
  mutate(group = factor(group, levels = names(table(data_coef$group)), labels = c("Group 1", "Group 2")))

  # make ribbon data y = slope*x + intercept for ci for slopes 
  ribbondata <- bind_rows(
    data.frame(
    x = seq(from = x_limits[1] - 1,  
            to = x_limits[2] + 1, 
            by = .05), 
    group = unique(graph.data$group)[1]
  ) %>% 
    mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
                 slice_head() %>% pull(estimate) * x) - 
             (cutoff*graph.data %>% filter(op == "=~") %>% 
                    slice_head() %>% pull(std.error)) +
             graph.data %>% filter(op == "~1") %>% 
                 slice_head() %>% pull(estimate), 
           ymax = (graph.data %>% filter(op == "=~") %>% 
                 slice_head() %>% pull(estimate) * x) + 
             (cutoff*graph.data %>% filter(op == "=~") %>% 
                    slice_head() %>% pull(std.error)) +
             graph.data %>% filter(op == "~1") %>% 
                 slice_head() %>% pull(estimate)), 
    data.frame(
      x = seq(from = x_limits[1] - 1,  
              to = x_limits[2] + 1, 
              by = .05), 
      group = unique(graph.data$group)[2]
    ) %>% 
      mutate(ymin = (graph.data %>% filter(op == "=~") %>% 
                   slice_tail() %>% pull(estimate) * x) - 
               (cutoff*graph.data %>% filter(op == "=~") %>% 
                      slice_tail() %>% pull(std.error)) +
               graph.data %>% filter(op == "~1") %>% 
                   slice_tail() %>% pull(estimate), 
             ymax = (graph.data %>% filter(op == "=~") %>% 
                   slice_tail() %>% pull(estimate) * x) + 
               (cutoff*graph.data %>% filter(op == "=~") %>% 
                      slice_tail() %>% pull(std.error)) +
               graph.data %>% filter(op == "~1") %>% 
                   slice_tail() %>% pull(estimate))
  )

  # make point data to draw on the intercepts 
  pointdata <- data.frame(
  x = c(0,0),
  y = graph.data %>% filter(op == "~1") %>% pull(estimate), 
  group = graph.data %>% filter(op == "~1") %>% pull(group),
  ymin = graph.data %>% filter(op == "~1") %>% pull(estimate) - 
    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error), 
  ymax = graph.data %>% filter(op == "~1") %>% pull(estimate) + 
    cutoff * graph.data %>% filter(op == "~1") %>% pull(std.error)
  )

  # make the line data to draw on the slopes
  linedata <- data.frame(
  slope = graph.data %>% filter(op == "=~") %>% pull(estimate), 
  intercept = graph.data %>% filter(op == "~1") %>% pull(estimate), 
  group = graph.data %>% filter(op == "~1") %>% pull(group)
  )

  # make the distributions for the residuals 
  violindata <- data.frame(
  y = c(rnorm(n = 1000, 
            mean = graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(estimate), 
            sd = graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(std.error)), 
        rnorm(n = 1000, 
            mean = graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(estimate), 
            sd = graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(std.error))),
  group = c(rep(graph.data %>% filter(op == "~~") %>% 
              slice_head() %>% pull(group), 1000),
            rep(graph.data %>% filter(op == "~~") %>% 
              slice_tail() %>% pull(group), 1000)), 
  x = 1
  )

  # make the latent mean data for right panel
  latent_predict <- predict(model_results)
  latent_means <- data.frame(
    c(latent_predict[[1]], latent_predict[[2]])
    )
  colnames(latent_means) <- colnames(latent_predict[[1]])
  latent_means$group <- rep(names(latent_predict), 
                  times = c(length(latent_predict[[1]]), 
                           length(latent_predict[[2]])))

  latent_means$lv <- latent_means[ , lv_name]

  # make a plot of the variance
  variance_plot <- 
  ggplot(violindata, aes(x = 1, y = y, color = group, fill = group)) + 
  geom_split_violin() + 
  theme_void() + 
  theme(legend.position = "none") + 
  stat_summary(fun = "mean",
               geom = "crossbar", 
               width = 0.5,
               colour = "black")

  # make the plot with intercepts and slopes
  intercept_plot <- 
  ggplot() + 
  # basic set up
  theme_classic() + 
  xlab("Latent Variable") + 
  ylab("Observed Variable") + 
  coord_cartesian(xlim = x_limits, ylim = y_limits) + 
  # plot the intercepts 
  geom_point(data = pointdata, 
             aes(x = x, y = y, color = group), 
             inherit.aes = FALSE) + 
  geom_errorbar(data = pointdata,
                aes(x = x, ymin = ymin, ymax = ymax, color = group), 
                inherit.aes = FALSE, width = .10) + 
  # plot the slopes
  geom_abline(data = linedata,
              aes(slope = slope, intercept = intercept, color = group)) + 
  geom_ribbon(data = ribbondata, 
              aes(x = x, ymin = ymin, ymax = ymax, fill = group), 
              inherit.aes = FALSE, alpha = .2) + 
  scale_color_discrete(name = "Group") + 
  scale_fill_discrete(name = "Group") + 
  geom_vline(xintercept = 0) + 
  theme(axis.line.y = element_blank())

  # make the latent means plot
  mean_plot <- ggplot(latent_means, aes(x = lv, fill = group)) + 
    geom_density(alpha = .2) + 
    theme_classic() + 
    xlab("Latent Variable") + 
    ylab("Density") + 
    geom_vline(data = latent_means %>% group_by(group) %>% summarize(mean = mean(lv)), 
               aes(xintercept = mean, color = group)) + 
    theme(legend.position = "none")

  y_range = abs(y_limits[2] - y_limits[1])

  # line up the two plots 
  prow <- plot_grid(
    intercept_plot + 
      theme(legend.position = "none") + 
      annotation_custom(ggplotGrob(variance_plot), 
                        xmin = .25, xmax = 1, 
                        ymin = y_limits[1], ymax = y_limits[2]-y_range/1.8),
    mean_plot + 
      theme(legend.position = "none"),
    align = 'vh',
    hjust = -1,
    nrow = 1
  )

  # get the lengend
  legend_b <- get_legend(
    intercept_plot + 
      guides(color = guide_legend(nrow = 1)) +
      theme(legend.position = "bottom")
  )

  # send out the plot 
  plot_grid(prow, legend_b, ncol = 1, rel_heights = c(1, .1))

}
```

@@

By the end of this tutorial manuscript, readers will:

1.  Be able to create visualizations for common steps to multi-group confirmatory factor analysis.
2.  Be able to interpret the impact and size of potential non-invariance on measurement.
3.  Understand the impact of measurement variability on replication and generalizability.

# Method

## Design and Analysis

Data was simulated using the `simulateData` function in the *R* package `lavaan` [@rosseel2012] assuming multivariate normality using a $\mu$ of 0 and $\sigma$ of 1 for the data. This function allows you to write `lavaan` syntax for your model with estimated values to generate data for observed variables. The data included two groups of individuals ("Group 1", "Group 2") for a multi-group confirmatory factor analysis (\$n\_{group}\$ = 250, *N* = 500). The latent variables were assumed to be continuous normal. The model consisted of five observed items predicted by one latent variable (`lv =~ q1 + q2 + q3 + q4 + q5`); however, the demonstration in this manuscript extends to multiple latent variables and other combinations of observed variables. Each item was assumed to be related to the latent variable with loadings approximately equal to .40 to .80, except when cases of non-invariance on the loadings was assumed.

The @brown2015 steps of testing measurement invariance are demonstrated in this manuscript for illustration purposes, but in line with @stark2006 suggestions, the visualizations show the impact of loadings and intercepts together. The configural model was analyzed nesting both groups into the same CFA model requiring that both groups show the same model structure, but all other parameters are free to vary between groups. The metric model constrained the factor loadings of each group to be equal within the model. The scalar model then constrained the item intercepts (i.e., item mean) to be equal across groups. Finally, the strict model constrained the item variances (i.e., error variances) to be equal for each item across groups. These models are normally tested sequentially, and a convenience function `mgcfa` is provided in the supplemental documents for this manuscript.

The data was then simulated to represent invariance across all model steps, small, medium, and large invariance using $d_{MACS}$ estimated sizes from @nye2019. While $d_{MACS}$ is used primarily for an effect size of the (non)-invariance for intercepts and loadings together, a similar approach was taken for the estimation of small, medium, and large effects on the residuals. The effect size is presented for all models, calculated from the *dmacs* package [@dueber2023, @nye2011]. Only one item in each model was manipulated from the invariant model to create the non-invariant models.

```{r create-models}
# overall model
model.overall <- "lv =~ q1 + q2 + q3 + q4 + q5"

# build invariant model one factor
model.invariant.g1 <- "lv =~ .8*q1 + .4*q2 + .6*q3 + .3*q4 + .6*q5 
q4 ~~ 1*q4
q4 ~ 0*1"
model.invariant.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .3*q4 + .61*q5
q4 ~~ 1*q4
q4 ~ 0*1"

# loadings
model.small.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .5*q4 + .61*q5"
model.med.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .6*q4 + .61*q5"
model.large.load.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + 1.1*q4 + .61*q5"

# build invariance on intercepts .25, .50, and .75
model.small.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~ .25*1"
model.med.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~ .5*1"
model.large.int.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~ .75*1"

# build invariance on residuals .25, .50, and .75
model.small.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~~ .75*q4"
model.med.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~~ .5*q4"
model.large.res.g2 <- "lv =~ .77*q1 + .43*q2 + .58*q3 + .34*q4 + .61*q5
q4 ~~ .25*q4"
```

```{r create-data}
# simulate data invariant
df.invariant <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.invariant.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data small load
df.small.load <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.small.load.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data med load
df.med.load <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.med.load.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data large load
df.large.load <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.large.load.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data small int
df.small.int <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.small.int.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data med int
df.med.int <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.med.int.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data large int
df.large.int <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.large.int.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data small res
df.small.res <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.small.res.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data med res
df.med.res <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.med.res.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)

# simulate data large res
df.large.res <- bind_rows(
  simulateData(model.invariant.g1, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 1"), 
  simulateData(model.large.res.g2, sample.nobs = 250, 
               meanstructure = T, model.type = "cfa",
               seed = 1234) %>% 
    mutate(group = "Group 2") 
)
```

```{r run-cfa}
# invariant CFA
results.invariant <- mgcfa(df.invariant, "group", model.overall)
d_invariant <- lavaan_dmacs(results.invariant$model.configural, RefGroup = "Group 1")

# loadings
results.small.load <- mgcfa(df.small.load, "group", model.overall)
results.med.load <- mgcfa(df.med.load, "group", model.overall)
results.large.load <- mgcfa(df.large.load, "group", model.overall)

d_small_load <- lavaan_dmacs(results.small.load$model.configural, RefGroup = "Group 1")
d_med_load <- lavaan_dmacs(results.med.load$model.configural, RefGroup = "Group 1")
d_large_load <- lavaan_dmacs(results.large.load$model.configural, RefGroup = "Group 1")

# intercepts
results.small.int <- mgcfa(df.small.int, "group", model.overall)
results.med.int <- mgcfa(df.med.int, "group", model.overall)
results.large.int <- mgcfa(df.large.int, "group", model.overall)

d_small_int <- lavaan_dmacs(results.small.int$model.configural, RefGroup = "Group 1")
d_med_int <- lavaan_dmacs(results.med.int$model.configural, RefGroup = "Group 1")
d_large_int <- lavaan_dmacs(results.large.int$model.configural, RefGroup = "Group 1")

# residuals
results.small.res <- mgcfa(df.small.res, "group", model.overall)
results.med.res <- mgcfa(df.med.res, "group", model.overall)
results.large.res <- mgcfa(df.large.res, "group", model.overall)

d_small_res <- lavaan_dmacs(results.small.res$model.configural, RefGroup = "Group 1")
d_med_res <- lavaan_dmacs(results.med.res$model.configural, RefGroup = "Group 1")
d_large_res <- lavaan_dmacs(results.large.res$model.configural, RefGroup = "Group 1")
```

```{r invariant-pic, include = T, fig.cap = "Invariant Model Visualization"}
plot_mgcfa(
  data_coef = results.invariant$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.invariant$q4), max(df.invariant$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.invariant$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r small-load-pic, include = T, fig.cap = "Small Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.small.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.load$q4), max(df.small.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-load-pic, include = T, fig.cap = "Medium Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.med.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.load$q4), max(df.med.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-load-pic, include = T, fig.cap = "Large Loadings Model Visualization"}
plot_mgcfa(
  data_coef = results.large.load$model_coef, # output from model_coef
  model_step = "configural", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.load$q4), max(df.large.load$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.load$model.configural, # what model results do you want 
  lv_name = "lv"
)
```

```{r small-int-pic, include = T, fig.cap = "Small Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.small.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.int$q4), max(df.small.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-int-pic, include = T, fig.cap = "Medium Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.med.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.int$q4), max(df.med.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-int-pic, include = T, fig.cap = "Large Intercepts Model Visualization"}
plot_mgcfa(
  data_coef = results.large.int$model_coef, # output from model_coef
  model_step = "metric", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.int$q4), max(df.large.int$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.int$model.metric, # what model results do you want 
  lv_name = "lv"
)
```

```{r small-res-pic, include = T, fig.cap = "Small Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.small.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.small.res$q4), max(df.small.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.small.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r med-res-pic, include = T, fig.cap = "Medium Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.med.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.med.res$q4), max(df.med.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.med.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

```{r large-res-pic, include = T, fig.cap = "Large Residuals Model Visualization"}
plot_mgcfa(
  data_coef = results.large.res$model_coef, # output from model_coef
  model_step = "scalar", # which model
  item_name = "q4", # name of observed item
  x_limits = c(-1,1), # LV limits to graph
  y_limits = c(min(df.large.res$q4), max(df.large.res$q4)), # Y min and max in data 
  ci_level = .95, # what ci do you want
  model_results = results.large.res$model.scalar, # what model results do you want 
  lv_name = "lv"
)
```

@@

# Appendix

```{r}
apa_table(results.invariant$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Invariant Model")
```

```{r}
apa_table(results.small.load$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Loadings")
```

```{r}
apa_table(results.med.load$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Loadings")
```

```{r}
apa_table(results.large.load$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Loadings")
```

```{r}
apa_table(results.small.int$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Intercepts")
```

```{r}
apa_table(results.med.int$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Intercepts")
```

```{r}
apa_table(results.large.int$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Intercepts")
```

```{r}
apa_table(results.small.res$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Small Differences in Residuals")
```

```{r}
apa_table(results.med.res$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Medium Differences in Residuals")
```

```{r}
apa_table(results.large.res$model_fit %>% 
            select(model, AIC, BIC, cfi, tli, rmsea, srmr), 
          col.names = c("Model", "AIC", "BIC", "CFI", "TLI", "RMSEA", "SRMR"),
          caption = "Model Fit for Large Differences in Residuals")
```
